### 2020-04-17 serial.tex
caption

\begin{figure}[!th]
\includegraphics[width=\textwidth]{forward_tease.pdf}
\caption{
\textbf{Effects of dynamical correlations between incubation periods and the number of secondary cases on serial intervals.}
}
\label{fig:tease}
\end{figure}

>>>>

\begin{figure}[!th]
\includegraphics[width=\textwidth]{forward_tease.pdf}
\caption{
\textbf{Dynamical correlations between incubation periods and the number of secondary cases.}
A. The mean forward serial interval depends on changes in the cohort reproduction number.
B. The mean backward incubation period of infectors is higher than the mean backward incubation period of all symptomatic cases.
C. Correlation between the number of secondary cases and the incubation period for individuals who got infected within the same time preiod.
D. Correlation between the number of secondary cases and the incubation period for individuals who developed symptoms within the same time preiod.
}
\label{fig:tease}
\end{figure}
